UKB Models

### 2023-10-06 ukb_mods.Rmd
all sigma betas

Seems like stepGAICAll handles combined sex.age term better than an interaction
Try adding TBV
```{r}
m3.tbv <- gamlss(formula = GMV ~ pb(age_days) + sex + fs_version + pb(sex.age) + pb(TBV),
                       sigma.formula = ~  pb(age_days) + sex,
                       nu.formula = ~ 1,
                       control = gamlss.control(n.cyc = 200), 
                       family = BCCG, data=ukb_df, trace = FALSE)
m4.tbv <- stepGAICAll.A(m3, scope=list(lower=~1, upper=~pb(age_days) + sex + fs_version + pb(sex.age) + pb(TBV)), k=2, glim.control(cyc=100)) #AIC
summary(m4.tbv)
```

@@

>>>>

Seems like stepGAICAll handles combined sex.age term better than an interaction
Try adding TBV
```{r}
m3.tbv <- gamlss(formula = GMV ~ pb(age_days) + sex + fs_version + pb(sex.age) + pb(TBV),
                       sigma.formula = ~  pb(age_days) + sex,
                       nu.formula = ~ 1,
                       control = gamlss.control(n.cyc = 200), 
                       family = BCCG, data=ukb_df, trace = FALSE)
m4.tbv <- stepGAICAll.A(Ventricles_mod, scope=list(lower=~1, upper=~pb(age_days) + sex + fs_version + pb(sex.age) + pb(TBV)), k=2, glim.control(cyc=100)) #AIC
summary(m4.tbv)
```

@@

### Sex-effects visualization

load info parsed from models via  `var_parse.sh` (which calls `R_scripts/variance_parser.R`)

```{r}
sigma.df <- read.csv(file="ukb/sigma.csv", row.names=1)
skim(sigma.df)
```

all contain sex in sigma

```{r}
sigma.df<- sigma.df %>%
  mutate(mu_form = as.factor(sub(".*~", "", mu_form)),
         sig_form = as.factor(sig_form),
         nu_form = as.factor(nu_form),
         measure_type = as.factor(case_when(grepl("Vol", region) ~ "Vol",
                                  grepl("CT", region) ~ "CT",
                                  grepl("SA", region) ~ "SA",
                                  TRUE ~ "Global")))

table(sigma.df$sig_form)
table(sigma.df$mu_form)
table(sigma.df$nu_form)
```

Weirdly only nu has variation in terms selected...?

plot sex effects in sigma
```{r}
ggplot(sigma.df, aes(x=sexMale, fill=measure_type)) +
  geom_histogram(alpha=0.6, position = "identity", color="white")
```

Normalize sexMale's beta weight by the overall value of all sigma terms

```{r}
#get betas
file.list <- list.files(path="/Users/megardn/Desktop/BGD_Repos/combat_biovar/ukb/gamlss_objs", pattern="_mod.rds", full.names = TRUE)

betas.mat <- sapply(file.list, get.moment.betas, moment="sigma", USE.NAMES=TRUE)
colnames(betas.mat) <- map(colnames(betas.mat), basename)
